Modern Graph Generators: A Survey

### 2018-11-09 generators_LinkedData.tex
typo

\paragraph{SP$^2$Bench} The SP$^2$Bench\footnote{\url{http://dbis.informatik.uni-freiburg.de/forschung/projekte/SP2B/}} is a language-specific benchmark~\cite{Schmidt2010} which is based on the DBLP  the dataset. %, so the types involve Person, Inproceedings, Article etc.
The generated datasets follow the key characteristics of the original DBLP dataset. In particular, the data mimics the correlations between entities. All random functions of the generator is based on a fixed seed that ensures the data generation process to be deterministic. SP$^2$Bench is accompanied by 12 queries covering different operator constellations such as RDF access paths and typical RDF constructs.

>>>>

\paragraph{SP$^2$Bench} The SP$^2$Bench\footnote{\url{http://dbis.informatik.uni-freiburg.de/forschung/projekte/SP2B/}} is a language-specific benchmark~\cite{Schmidt2010} which is based on the DBLP dataset. %, so the types involve Person, Inproceedings, Article etc.
The generated datasets follow the key characteristics of the original DBLP dataset. In particular, the data mimics the correlations between entities. All random functions of the generator is based on a fixed seed that ensures the data generation process to be deterministic. SP$^2$Bench is accompanied by 12 queries covering different operator constellations such as RDF access paths and typical RDF constructs.
